1. Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100
&amp; generate another 6x6 matrix (B) using random numbers between 500 to 600.
```{r}
# Generate Matrix A and B

# Generate 36 random numbers for matrix A
a = floor(runif(36, min=1, max=100))
# Create Matrix A
A = matrix(a, 6, 6)
A
# Generate 36 random numbers for matrix B
b = floor(runif(36, min=500, max=600))
# Create Matrix A
B = matrix(b, 6, 6)
B

```
a. Find the range of matrices A and B.
b. Find the max value from each row of the matrices A and B.
c. Find the diagonal values of matrices A&amp;B.
d. Multiply matrices A and B
e. Replace the 4th row of Matrix A with diagonal values of matrix B
f. Multiply matrices A &amp; B and store the values on X.
g. Divide the matrix A with matrix B.
```{r}
# a. Find Range of matrices

## range of matrix A
i = 0
while(i <=6){
  print(A[,i])
  i = i+1
}
## range of matrix B
i = 0
while(i <=6){
  print(B[,i])
  i = i+1
}

# b. Find max value of each row
# Matrices A
i= 1
print("Max value of each row of Matrix A")
while(i <=6){
  print(max(A[i,]))
  i = i+1
}

print("Max value of each row of Matrix B")
i = 0
while(i <= 6){
  print(max(B[i,]))
  i = i+1
}

#c. Find Diagonal values
diag(A)
diag(B)

#d. Multiply Matrix A and B 
A %o% B

#e. Replace 4th row of A with Diagonal value of B
A[4,] <- diag(B)
A

#f. Multiply matrices A &amp; B and store the values on X.
X = A %o% B
X

#g. Divide the matrix A with matrix B.
invB = solve(B)
division = A * invB
division
```

2. Create a table using dataframe/tibble with the following categories(a to f)
a. First name,
b. Second Name,
c. Age,
d. Occupation,
e. Place,
f. Random numbers( between 1 to 10)
```{r}
# Create 10 observations
firstname <- c("Chea", "Kim", "muny", "Ley", "Sreng", "Sok", "Sao", "Som", "Hok", "Lay")
secondname <- c("Vorn", "Teng", "Lim", "Sovann", "Vuthy", "Nara", "Seng", "Ly", "Kimghak", "King")
age <- c(20, 21, 23, 40, 19, 19, 35, 20, 25, 21)
occupation <- c("Student", "Student", "Student", "Teacher", "Student", "Student", "Teacher", "Student", "Student", "Student")
place <- c("KIT", "Phnom Penh", "KIT", "KIT", "Phnom Penh", "KIT", "Phnom Penh", "KIT", "KIT", "KIt")
# generate 10 random numbers
rannum <- floor(runif(10, min=1, max=10))

# Create the dataframe
mydata <- data.frame(FirstName = firstname, SecondName = secondname, Age=age, Occupation = occupation, Place = place, randomnum = rannum  )
mydata 
```
g. Extract the last column (f)
h. Find the sum, mean and length of the extracted column
```{r}
# g. extract the last column (f)
library(dplyr)
lastcol = transmute(mydata, randomnum)
lastcol
# h. Find sum, mean, length of the extract column
## sum
sum(lastcol)
## mean
mean(unlist(lastcol))
## length
length(lastcol)
count(lastcol)

```
3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from
the official news agency’s website(Note: Include the reference link) and do the following
a. Read the .txt file
b. Perform the Tokenization &amp; count the words
c. Identify the most repeated word and replace that word with “KIT”
d. Perform the Sentiment analysis
e. Plot the graph between “words count” and “words” using geom_col()

e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color,
Center, space between graph and title = 20.

e.2. Y-axis title =“List of words”, Size=10, Bold, Text in Red color,
Center, space between graph and title = 20.
e.3. Graph title =”Text Mining using R”,Size = 25, Bold, Center, Text in
Yellow color, space between graph and title = 25.

```{r}
# reference link: https://www.phnompenhpost.com/national-post-depth/economic-woes-back-home-migrants
# a. Read the .txt file
news_data <- read.delim("C:/Users/KIT/Documents/R/khmer_news.txt", header=F)
news_data

```
```{r}
# b. perform tokenization and count the words
library(tidytext) # for tokenization
library(ggplot2) # for graph visualization
library(dplyr)
dataset <- data.frame(S.No=1, Text=as.vector(news_data))
dataset
dataset %>% 
  unnest_tokens(Info, Text) %>%
  count(Info, sort=TRUE) %>% 
  ggplot(aes(n, Info)) + geom_col() # plot the graph using ggplot2

```

```{r}
# C. Find the most frequent word and replace it with "KIT"

```


```{r}
# d. Perform sentiment analysis 

library(pacman)
pacman::p_load(sentimentr)

num <- 1:7
paragraph <- c("A", "B", "C", "D", "E", "F", "G")
table <-data.frame(V1=news_data, Num=num, Title=paragraph)
table

result1<- sentimentr::sentiment(table$V1) # To know number of sentences and words(Sentiment at the sentence level)
result1
result2 <-sentiment_by(table$V1) # Total number of words
result2
result3<- get_sentences(table) # To display the sentences
result3
result4<- emotion(table$V1) # Emotion at the sentence level
result4
result5<- emotion_by(table$V1) # Aggregated emotion by group(s)
result5
result6<- profanity(table$V1) # Profanity at the sentence level
result6
result7<- profanity_by(table$V1) # Aggregated profanity by group(s)
result7
```

4. Find the assigned Dataset from the list below and perform the following (20 Marks)
a. Import and Clean the dataset.
b. Find the x and y variables(axis) from the assigned dataset and give the reason for
selecting the x and y axis.
c. Plot the graph using geom_col() and perform the linear model in statistics.
d. Perform the facet with the available columns(Choose the any two variables from the
columns)
e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis &amp;
graph)
e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space
between graph and title = 20.
e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space
between graph and title = 20.
e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space
between graph and title = 25.
```{r}
# a. Import data and clean it
data <- read.csv("C:/Users/KIT/Documents/R/drinks.csv")
data
```


b. Find x and y
- x variable is "country": because it mainly acts as the key identifer and give the information of the country that consume a specific amount of alcohol.
- y variable is "total_litre_of_pure_alcohol": because from this data, we can know which country consume which total amount of alcohol in litres. The graph will match from the country name to the exact total amount of alchohol consumed by the country.
- From the graph, we can identify which country should we start the alchohol business in, or which country that consume the least amount of alcohol so that we should give less priority. 
- Also, we can know if the country consume the most amount of alcohol, what are the major problems that occurs in that country accordingly.
```{r}
# c. Plot the graph using geom_col() and perform the linear model in statistics.
library(ggplot2)
plot <- ggplot(data , mapping = aes(x= country, y=total_litres_of_pure_alcohol)) +
      geom_point(size=3, alpha) +
      geom_smooth(method="glm")
# d. perform facet
plot <- plot + facet_grid(beer_servings ~ spirit_servings)
# e. Edit the layer
plot <- plot + 
      xlab("Countries") +
      ylab("Total alchohol consumption") +
    ggtitle("Worldwide Alcohol Consumption Data") +
    theme(axis.title.x=element_text(size=15, color="green", face="bold", margin=margin(t=20,r=20,b=0,l=0)),
          axis.title.y=element_text(size=15, color="yellow", face="bold", margin=margin(t=0,r=20,b=0,l=20)),
          plot.title=element_text(size=15, color="blue", face="bold", margin=margin(t=20,r=0,b=25,l=0)))
```



